An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
Clean up section on temporal paths

The key new idea in generalizing BFS to evolving graphs is to be able to compute
traversals that span multiple times. We call some, but not all,
such traversals \textit{temporal paths}.

@@

The restriction that temporal paths may only traverse active nodes reflects
underlying structure in many real world applications, such as analyzing influence
of nodes over social networks, and furthermore leads to interesting and nontrivial
adaptations of graph algorithms such as BFS

>>>>

The key new idea in generalizing BFS to evolving graphs is to be able to compute
paths that traverse multiple times. We call the relevant paths
\textit{temporal paths}.

@@

The restriction that temporal paths may only traverse active nodes reflects
underlying structure in many real world applications, such as analyzing the
influence of nodes over social networks. We will also show later in
%XXX FIX X-REF TO SECTION
that the resulting structure of allowable temporal paths leads to nontrivial
subtitled in the generalization of algorithms and concepts from ordinary
(static) graphs.
